\documentclass[13pt]{letter}
\renewcommand{\baselinestretch}{1.3}\normalsize
\usepackage{setspace}\doublespacing
\usepackage{hyperref}
\usepackage[a4paper,left=3.5cm, right=3.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\signature{Philipp Eisenhauer}
\address{Institute for Applied Microeconomics \\ University of Bonn \\ Lenn\'{e}str. 43
 \\ 53113 Bonn \\ Germany}
\begin{document}

\begin{letter}{Prof. Badi H. Baltagi \\Department of Economics \\
426 Eggers Hall, Syracuse University \\
Syracuse, New York 13244-1020\\
United States }

\opening{Dear Prof. Baltagi:}

Thank you very much for considering my submission \textit{The Approximate Solution of Finite-Horizon Discrete Choice Dynamic Programming Models} for the \textit{Replication Section} in the \textit{Journal of Applied Econometrics (JAE)}.

This manuscript is supplemented by an open-source Python package for the simulation and estimation of a prototypical discrete choice dynamic programming model. It is available at \url{http://respy.readthedocs.io}.

I very much hope that you consider publishing detailed replications of major structural econometric articles in the \textit{JAE}. It provides young researchers with a unique learning opportunity to tackle these often complex research projects in a controlled setting and increases the level of transparency about computational details. Of course, I would be glad to serve as a referee for such future submissions. I attach my curriculum vitae as a reference.

If you have any further questions or comments, please do not hesitate to contact me.\newline

\closing{Yours Faithfully,}\vspace{0.5cm}

\end{letter}

\end{document}
\grid
