%-------------------------------------------------------------------------------
\section{Recomputation Instructions}
%-------------------------------------------------------------------------------
I provide an image of a virtual machine (VM) for download to ensure full recomputability of my results. The image contains a software-based emulation of a computer, where all the required software is already pre-installed. This makes recomputation straightforward.\\\newline
%
Two additional software tools are required: (1)  \texttt{VirtualBox} and (2) \texttt{Vagrant}. \texttt{VirtualBox} is a virtualization software, while \texttt{Vagrant} provides a convenient wrapper around it. Both are free and open-source. Please consult their websites for installation instructions. The following instructions were tested for \texttt{VirtualBox 5.0} and \texttt{Vagrant 1.8}.\newline

Once \texttt{VirtualBox} and \texttt{Vagrant} are available, the image can be downloaded and accessed by the following commands:

\vspace{0.2cm}\begin{lstlisting}[language=bash]
    $ vagrant init structRecomputation/base
    $ vagrant up --provider virtualbox
    $ vagrant ssh
\end{lstlisting}\vspace{0.2cm}

As all the required software is already installed, recomputation is straightforward. Simply typing the following command into the terminal produces all the results in the paper:
\vspace{0.2cm}\begin{lstlisting}[language=bash]
    $ ./recompute
\end{lstlisting}\vspace{0.2cm}

The output files will be available in the \verb+_published+ subdirectory. This process takes a couple of days due to the large number of Monte Carlo iterations for the initial Monte Carlo exercise. There is a slight difference in the order and sign of the coefficients between the output files and the results in this paper, please see  \verb+respy+'s online documentation for details. Table \ref{Mapping} provides the mapping between the output files and the results reported in the two relevant publications.

\input{../material/table_mappings.tex}
